### 2020-06-24 Strings2020/strings7/strings7.tex
Finish strings7

\item \textbf{Two and Three-Point Functions in AdS/CFT}

>>>>

\item \textbf{Two and Three-Point Functions in AdS/CFT}
\def\adsFive/{$\mrm{AdS}_5$}

	Consider a scalar field $\phi(x,z)$ in Poincar\'e \adsFive/ (with radius $R = 1$) satisfying:
	\begin{equation}
		\pqty{\laplacian - m^2}\,
			\phi(x,z) = 0,
	\quad
		\phi(x,z) \to
		\left\lbrace\vbox to 12.5pt {}\right.
		\begin{aligned}
			& z^\delta \phi_0(x)\,,
				&& z\to 0, \\[-.35ex]
			& \mrm{regular},
				&& z\to\infty,
		\end{aligned}
	\quad
		\delta = 2 - \sqrt{m^2 + 4}
	\end{equation}
	It can be constructed via the boundary-to-bulk propagator $K_\Delta$:
	\begin{gather}
		\phi(x,z)
		= \int \dd[4]{x'}
			K_\Delta(x,z;x')\,
			\phi(x'),
	\\
		K_\Delta(x,z;x')
		= \frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
			\pqty{\frac{z}{
				z^2 + \norm{x - x'}^2
			}}^{\!\!\Delta},
	\quad
		\Delta = 2 + \sqrt{m^2 + 4}
	\end{gather}

	\begin{enumerate}
	\item To verify this, we first check that the boundary conditions are indeed satisfied by $K_\Delta$; note that $\Delta \ge 2 > 0$, and we have:
	\begin{equation}
		z\to 0,\quad l \ne 0,
	\quad
		\pqty{\frac{z}{
			z^2 + l^2
		}}^{\!\!\Delta} \to 0,
	\end{equation}
	i.e.\ the only contribution comes from the $l\to 0$ case, where we have:
	\begin{equation}
	\begin{aligned}
		l = \norm{x - x'} \to 0,
	\quad
		\int \dd[4]{x'}
			K_\Delta(x,z;x')
		&= \frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
			\int_0^\infty 2\pi^2 l^3 \dd{l}
				\pqty{\frac{z}{
					z^2 + l^2
				}}^{\!\!\Delta} \\
		&= \frac{(\Delta - 1)(\Delta - 2)}{\pi^2}\cdot
			\frac{2\pi^2}{2\,(\Delta - 1)(\Delta - 2)}\,
			z^{4 - \Delta} \\
		&= z^\delta
	\end{aligned}
	\end{equation}
	Therefore, we have:
	\begin{equation}
		z \to 0,
	\quad
		K_\Delta(x,z;x')
		\to z^\delta \delta^4(x - x'),
	\quad
		\phi(x,z)
		\to z^\delta \phi_0(x),
	\end{equation}
	The other boundary condition is convenient to check; we have:
	\begin{equation}
		z \to \infty,
	\quad
		K_\Delta(x,z;x')
		\propsim z^{-\Delta} \to 0,
	\quad
		\phi(x,z)
		\,\ \text{regular.}
	\end{equation}

	Now we need only check that $K_\Delta$ satisfies the equation of motion; in Poincar\'e \adsFive/ we have:
	\begin{equation}
		\laplacian
		= z^2 \pqty{
				\pdd{z}^2
				- \frac{3}{z}\, \pdd{z}
				+ \pdd{x}^2
			}
	\end{equation}
	With the help of Mathematica\textsuperscript{TM}, it is straightforward to check that $
		\pqty{\laplacian - m^2}\,
			\pqty\big{\frac{z}{
				z^2 + l^2
			}}^{\Delta}
		= 0
	$, therefore $
		\pqty{\laplacian - m^2}\,
			\phi(x,z) = 0
	$.

	\newparagraph
	The AdS/CFT dictionary is given by:
	\begin{equation}
		\ave*{
			e^{
				\int\dd[4]{x}\,
					C_O\, \phi_0(x)\, O(x)
			}
		}_{\mrm{CFT}}
		= e^{-S[\phi_0]}
	\end{equation}
	Where $S[\phi_0]$ the bulk effective action evaluated on the solution to the equation of motion:
%	We have taken the classical limit in the RHS, since the AdS/CFT correspondence is a strong/weak duality; for a strongly coupled CFT the bulk theory is weakly coupled, 
	\begin{equation}
		S[\phi_0]
		= \int \dd[4]{x} \dd{z}
			\sqrt{-G}\,\Bqty{
				\frac{1}{2}\,\pqty{\pdd{\mu}\phi}^2
				+ \frac{1}{2}\,m^2 \phi^2
				+ \frac{1}{3}\,g \phi^3
				+ \cdots
			}
	\end{equation}

	\item The CFT 2-point function $
		\ave{O(x)\,O(y)}
	$ can be computed with the above dictionary, using the usual effective formalism, but with the bulk action instead of the boundary action:
	\begin{equation}
		\ave{O(x)\,O(y)}
		= \frac{1}{C_O^2}
			\eval{
				\frac{\var[2]}{
					\var{\phi_0(x)} \var{\phi_0(y)}
				}\, e^{-S[\phi_0]}
			}_{\phi_0=0}\!\!
	\end{equation}
	For 2-point function, we only need terms $\sim\order{\phi^2}$; note that:
	\begin{equation}
		\fdv{\phi(x,z)}{\phi_0(x')}
		= K_\Delta(x,z;x'),
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
	\begin{aligned}
		\var{S}[\phi_0]
		&\sim \int \dd[4]{x} \dd{z} \sqrt{-G}\,
				\pqty{-\laplacian + m^2}\,\phi \var{\phi}
			+ \int_{z\to 0} \dd[4]{x} \sqrt{-G}\,
				\pd^{z} \phi \var{\phi} \\
		&= 0 - \int_{z\to 0} \dd[4]{x}
				z^{-5} z^2
				\pdd{z} \phi \var{\phi}
		= -\int_{z\to 0} \dd[4]{x}
				z^{-3}
				\pdd{z} \phi \var{\phi},
	\end{aligned}
	\end{equation}
	\begin{equation}
	\begin{aligned}
		\therefore\quad
		\ave{O(x)\,O(y)}
		&= +\frac{1}{C_O^2}
			\eval{
				\frac{\var}{
					\var{\phi_0(x)}
				}\, e^{-S[\phi_0]}
				\int_{z\to 0} \dd[4]{x'} z^{-3}
					\pdd{z} \phi(x',z)\,
					K_\Delta(x',z;y)\,
			}_{\phi_0=0}\!\! \\
		&= \frac{1}{C_O^2}
				\int_{z\to 0} \dd[4]{x'} z^{-3}
					\pdd{z} K_\Delta(x',z;x)\,
					K_\Delta(x',z;y) \\
		&= \frac{1}{C_O^2}
				\int_{z\to 0} \dd[4]{x'} z^{-3}
					\pdd{z} K_\Delta(x',z;x)\,
					z^\delta \delta^4(x' - y) \\
		&= \frac{z^{\delta - 3}}{C_O^2}\,
			\pdd{z} K_\Delta(x,z;y) \\
		&\sim \frac{z^{\delta-3}}{C_O^2}\,
			\frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
			\frac{
				\Delta z^{\Delta-1}
			}{\norm{x - y}^{2\Delta}} \\
		&= \frac{1}{C_O^2}\,
			\frac{\Delta(\Delta - 1)(\Delta - 2)}{\pi^2}
			\frac{1}{\norm{x - y}^{2\Delta}} \\
	\end{aligned}
	\end{equation}

	Therefore, if we want $
		\ave{O(x)\,O(y)}
		= \frac{1}{\norm{x - y}^{2\Delta}}
	$, then we have\footnote{
		Reference: \arxiv{hep-th/9804058}. Again I would like to thank Lucy Smith for hints with this problem. 
	}:
	\begin{equation}
		C_O
		= \frac{1}{\pi} \sqrt{
				\Delta(\Delta - 1)(\Delta - 2)
			}
	\end{equation}
	Here $z\to 0$ is a cutoff parameter.

	\item Similarly, we can use the dictionary to compute 3-point functions; we have\footnote{
		Reference: \arxiv{hep-th/9905111}, and \arxiv{hep-th/9804058}. 
	}:
	\begin{equation}
		\ave{O(x_1)\,O(x_2)\,O(x_3)}
		= \frac{1}{C_O^3}\,
			\pqty{-\frac{g}{3}}
			\int \dd[4]{x} \dd{z} \sqrt{-G}\,
				K_\Delta(x,z;x_1)\,
				K_\Delta(x,z;x_2)\,
				K_\Delta(x,z;x_3)
	\end{equation}
	This is a difficult integral; as is suggested by \arxiv{hep-th/9804058}, we can use an important symmetry of AdS/CFT --- the inversion $
		\vec{x}\mapsto \frac{\vec{x}}{x^2}
	$, to complete the integration.

	By conformal symmetry, we know that the 3-point function is of the form:
	\begin{equation}
		\ave{O(x_1)\,O(x_2)\,O(x_3)}
		= A(x_1,x_2,x_3)
		= \frac{C_{OOO}}{
				\abs{x_{12}}^\Delta
				\abs{x_{23}}^\Delta
				\abs{x_{31}}^\Delta
			},\quad x_{ij} = x_i - x_j
	\end{equation}
	First set $x_3 = 0$, then perform inversion on all other points:
	\begin{gather}
		x_i = \frac{x'_i}{x'^2_i}, \quad
		(x,z) = \frac{(x',z')}{\,r'^2},
	\quad
		r^2 = x^2 + z^2,\quad
		r^2 r'^2 = 1 = x_i^2 x_i'^2,
	\\
		\frac{\dd[4]{x} \dd{z}}{z^5}
		= \frac{\dd[4]{x'} \dd{z'}}{z'^5},
	\\
	\begin{aligned}
		\frac{z}{z^2 + \norm{x - x_i}^2}
		&= \frac{z}{r^2 + x_i^2 - 2x\cdot x_i}
		= \frac{z'/r'^2}{
				1/r'^2 + 1/x'^2_i
				- 2x'\cdot x'_i/\pqty{r'^2 x'^2_i}
			} \\
		&= \frac{z'}{r'^2 + x'^2_i - 2x'\cdot x'_i}
			\,x'^2_i
		= \frac{z'}{z'^2 + \norm{x' - x'_i}^2}
			\,x'^2_i,
	\end{aligned}
	\\[1ex]
		K_\Delta(x,z;x_i)
		= K_\Delta(x',z';x'_i)\,\abs{x'_i}^{2\Delta}
		= \frac{1}{\abs{x_i}^{2\Delta}}\,
			K_\Delta(x',z';x'_i),
	\end{gather}
	With these in mind, we find that:
	\begin{equation}
		A(x_1,x_2,0)
		= -\frac{g}{3C_O^3}\,
			\frac{1}{\abs{x_1}^{2\Delta}}
			\frac{1}{\abs{x_2}^{2\Delta}}
			\frac{(\Delta - 1)(\Delta - 2)}{\pi^2}
		\int \frac{\dd[4]{x'} \dd{z'}}{z'^5}
			K_\Delta(x',z';x'_1)\,
			K_\Delta(x',z';x'_2)\,
			z'^\Delta
	\end{equation}
	The integral can then be completed using Feynman parameters; in the end we obtain:
	\begin{gather}
		A(x_1,x_2,0)
		\propto
			\frac{1}{\abs{x_1}^{2\Delta}}
			\frac{1}{\abs{x_2}^{2\Delta}}
			\frac{1}{\abs{x'_1 - x'_2}^{2\Delta}}
		= \frac{1}{
				\abs{x_1}^{\Delta}
				\abs{x_2}^{\Delta}
				\abs{x_1 - x_2}^{\Delta}
			},
	\\[1ex]
		C_{OOO}
		= -\frac{g}{3C_O^3}\,
			\frac{1}{2\pi^4}
			\pqty{
				\frac{\Gamma(\tfrac{\Delta}{2})}{
					\Gamma(\Delta - 2)
				}
			}^{\!\!3}
			\Gamma\pqty{
				\frac{3\Delta - 4}{2}
			}
	\end{gather}
